PRISM protocol v0.3

### 2023-07-25 docs/public-docs/article.tex
feat: remove deprecated projects and add new release process

\begin{itemize}
\item The user generates a desired list of public keys. He will associate each key to a key identifier and a role.
      There must be at least one key with the master role in this initial list.
\item The resulting list is encoded and hashed producing an encoded \emph{initial\_state} and a \emph{hash}.
\item The \emph{hash} is encoded in hexadecimal form producing an \emph{encoded\_hash}.
\item The user DID is constructed as \emph{did:prism:encoded\_hash}.
\item The user will send in the metadata of a blockchain transaction a signed \emph{CreateDID} event. 
      The event contains the list of public keys with their identifiers and roles.
      The signature will be performed using the private key associated to any of the master keys in the initial list of keys.
\end{itemize}

@@

When the event added to the blockchain with enough confirmations, all parties will process the event. This is, they will validate the signature, and update their internal knowledge of the updated DID. The newly added keys and the revoked keys will be timestamped using the time of the carrier transaction.

@@

In the following steps, we assume the issuer and subjects have already established a secure communication channel. We also assume that the issuer has
a published DID that will be used to represent him in credentials.
In order to issue a batch of an arbitrary number $N$ of credentials, the issuer will:
\begin{itemize}
\item Ask to each subject the DID they would like to use for the credential they will receive.
\item The issuer creates the credentials for each subject. It uses his published DID and the key id of an \emph{issuing key} to populate
      the credential corresponding fields. On each credential, it adds the corresponding subject DID as one of the claims.
\item The issuer encodes each individual credential using a base64URL encoding.
\item The issuer signs each individual encoded credential with an \emph{issuing key} associated to his publicly known DID. 
      The signing key corresponds to the key id in the credentials' claims.
\item The issuer encodes each signature, and concatenate them to their corresponding credentials using a dot (".") as separator.
      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings asa
      \emph{signed credentials}.
\item Now, the issuer takes all the signed credentials, and computes a merkle root from them.
\item The issuer creates an \emph{IssueBatch} event that contains the merkle root and issuer DID, and signs the event with an \emph{issuing key} associated to this DID. 
\textbf{Note}: Today we use the same issuing key for the event signature and the individual credentials signature, but those could be different keys.
\item The issuer attaches the signed event to the metadata of a transaction and sends it to the blockchain.
\item The issuer gives to each subject their corresponding signed credential along with their associated merkle inclusion proof.
\end{itemize}

>>>>

\begin{itemize}
\item The user generates a desired list of public keys. He will associate each key to a key identifier and a role.
      There must be at least one key with the master role in this initial list.
\item The resulting list is encoded and hashed producing an encoded \emph{initial\_state} and a \emph{hash}.
\item The \emph{hash} is encoded in hexadecimal form producing an \emph{encoded\_hash}.
\item The user's DID is constructed as \emph{did:prism:encoded\_hash}.
\item The user will a signed \emph{CreateDID} event in the transaction metadata that is submitted to a blockchain.
      The event contains the list of public keys with their identifiers and roles.
      The signature will be performed using the private key associated to any of the master keys in the initial list of keys.
\end{itemize}

@@

When the event added to the blockchain has enough confirmations, all parties will process the event. This is, they will validate the signature, and update their internal knowledge of the updated DID. The newly added keys and the revoked keys will be timestamped using the time of the carrier transaction.

@@

In the following steps, we assume the issuer and subjects have already established a secure communication channel. We also assume that the issuer has
a published DID that will be used to represent him in credentials.
In order to issue a batch of an arbitrary number $N$ of credentials, the issuer will:
\begin{itemize}
\item Ask to each subject the DID they would like to use for the credential they will receive.
\item The issuer creates the credentials for each subject. It uses his published DID and the key id of an \emph{issuing key} to populate
      the credential corresponding fields. On each credential, it adds the corresponding subject DID as one of the claims.
\item The issuer encodes each individual credential using a base64URL encoding.
\item The issuer signs each individual encoded credential with an \emph{issuing key} associated to his publicly known DID. 
      The signing key corresponds to the key id in the credentials' claims.
\item The issuer encodes each signature, and concatenates them to their corresponding credentials using a dot (".") as separator.
      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings \emph{signed credentials}.
\item Now, the issuer takes all the signed credentials, and computes a merkle root from them.
\item The issuer creates an \emph{IssueBatch} event that contains the merkle root and issuer DID, and signs the event with an \emph{issuing key} associated to this DID. 
\textbf{Note}: Today we use the same issuing key for the event signature and the individual credentials signature, but those could be different keys.
\item The issuer attaches the signed event to the metadata of a transaction and sends it to the blockchain.
\item The issuer gives to each subject their corresponding signed credential along with their associated merkle inclusion proof.
\end{itemize}
